Output Summary

### 2021-10-11 03-post-process/output-plots.Rmd
Rename model scenario to base
This is new best version of the model

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "complex-ocean-survival-with-prior"
    input: text
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---
